Hyper-linked Communications: WebRTC enabled asynchronous collaboration

### 2015-06-02 tese/project.tex
Added a few sentences to the abstract.

\begin{abstract}
Hyper-linked communications concept applies much of the hypermedia concepts, widely used on Web content, for communication and collaboration services. This paradigm allows to synchronize and structure the communications content, providing a way to integrate social media content and collaborative tools into voice and video calls.

Voice and image together can express emotions and expose creativity like no other medium can. With hypermedia concepts we can add more value to voice and video communications.

WebRTC technology, allows real-time communications between web browsers without being forced to install and use additional applications or plug-ins. The nature of web browser applications already follow the hypermedia concept, which makes WebRTC the ideal technology to apply the hyper-linked communications concepts.

The native support of WebRTC in operating systems extends its usage to outside the web browser, allowing to explore functionalities that browsers are poor to support such as video recording and massive information storage.

Our goal in this project is to develop an application that applies Hyper-linked communications concept using WebRTC.

>>>>

\begin{abstract}
The Hyper-linked communications concept applies much of the hypermedia concepts, widely used on Web content, to communication and collaboration services. This paradigm allows to synchronize, structure and navigate communication content, providing a way to integrate social media content and collaborative tools into voice and video calls.
Voice and image together can express emotions and expose creativity like no other medium can. With hypermedia concepts, we can add more value to voice and video communications.

WebRTC technology allows real-time communications between web browsers without the need to install and use additional applications or plug-ins. The nature of web browser applications already follow the hypermedia concept, which makes WebRTC the ideal technology to apply the hyper-linked communications concepts.
The native support of WebRTC in operating systems extends its usage to outside the web browser, allowing to explore functionalities that browsers are poor to support such as video recording and massive information storage.

Our goal in this project is to develop an application that leverages the Hyper-linked communications concept to enable colaborative real-time audio and video communication, enriched with other media types, that can be accessed live or accessed latter.
This application will target the web browser platform, resorting to WebRTC.

In this document, we present the current State Of The Art in hyper-linked communications and related technologies, propose an architecture to implemente an hyper-linked communication application based on WebRTC and provide a plan for its implementation and evaluation.
